\LARGE \bf Blockchain for routing correctness?

### 2018-08-04 BM-BGP.tex
small typo

There are other attacks on blockchain: nothing at stake attack (for POS), sybil attacks, and quantum computers. Briefly, nothing at stake is the problem that block producers do not have any incentive to choose one block, and therefore, will mine after any block as long as they are confident that the blocks before the one they are mining will be accepted by the network. The worry is that miners will mine on top of forks in order to increase the likelihood of a payout, and this does not solve the double spend problem. Sybil attacks occur when malicious nodes cut off honest nodes from the network (Heilman 2015), but it is hard to successfully do if the P2P network is interconnected well (from good seeding). Quantum computers are only a problem if the signature algorithms that are used in transactions are based on the discrete log problem (RSA or ECC) because Shor’s algorithm makes it computationally feasible to factor large numbers (Shor 1994). Hash functions are not as vulnerable to quantum computers as signatures are because key sizes only have to be doubled.

@@

The blockchain analyzed later in the paper is similar to Plasma in its use of merkle trees. For this reason, Plasma will be described here. Second layer solutions setup a “game” through contracts on-chain that have an outcome that can be determined with high probability from messages passed off-chain. \footnote{Author's note: this is paraphrased from a talk by Vitalik Buterin but the source is not known.} Plasma is a smart contract on-chain that allows a operator to submit blocks in a new chain inside of the ethereum chain. Blocks are only merkle roots of transactions in the simplest case (Buterin Minimum 2017). If someone deposits money on a plasma contract, they can send it to someone else without having the transaction move on-chain. The transaction only moves on-chain when a person claims to own X coins by calling exit() on the smart contract. There is a window of time for exits to be contested and if a new unspent transaction output (UTXO) in a more recent block is shown to exist along with the appropriate signatures then the exit fails. Plasma is similar to the blockchain proposed in this paper only in that merkle trees are used to confine validity checking of some information only to the nodes who are interested in consensus of that information.

>>>>

There are other attacks on blockchain: nothing at stake attack (for POS), sybil attacks, and quantum computers. Briefly, nothing at stake is the problem that block producers do not have any incentive to choose one block, and therefore, will mine after any block as long as they are confident that the blocks before the one they are mining will be accepted by the network. The worry is that miners will mine on top of forks in order to increase the likelihood of a payout, and this does not solve the double spend problem. Sybil attacks occur when malicious nodes cut off honest nodes from the network (Heilman 2015), but it is hard to successfully do if the P2P network is interconnected well (from good seeding). Quantum computers are only a problem if the signature algorithms that are used in transactions are based on the discrete log problem (ECC) or factoring (RSA) because Shor’s algorithm makes it computationally feasible to factor large numbers (Shor 1994). Hash functions are not as vulnerable to quantum computers as signatures are because key sizes only have to be doubled.

@@

The blockchain analyzed later in the paper is similar to Plasma in its use of merkle trees. For this reason, Plasma will be described here. Second layer solutions setup a “game” through contracts on-chain that have an outcome that can be determined with high probability from messages passed off-chain. \footnote{Author's note: this is paraphrased from a talk by Vitalik Buterin but the source is not known.} Plasma is a smart contract on-chain that allows an operator to submit blocks in a new chain inside of the ethereum chain. Blocks are only merkle roots of transactions in the simplest case (Buterin Minimum 2017). If someone deposits money on a plasma contract, they can send it to someone else without having the transaction move on-chain. The transaction only moves on-chain when a person claims to own X coins by calling exit() on the smart contract. There is a window of time for exits to be contested and if a new unspent transaction output (UTXO) in a more recent block is shown to exist along with the appropriate signatures then the exit fails. Plasma is similar to the blockchain proposed in this paper only in that merkle trees are used to confine validity checking of some information only to the nodes who are interested in consensus of that information.
